Turbulence in compact to giant HII regions

### 2022-05-12 strucfunc_paper.tex
Javier changes 2022-05-10

\begin{figure*}
  \centering
  \sffigggg{OrionS}{M8}{OrionLH}{CarC}
  \caption{
    Second-order structure functions
    for velocity centroid images
    of the \ha{} emission line
    from Galactic \hii{} regions.
    Blue symbols show the observed mean structure function
    in each radial bin.
  }
  \label{fig:strucfunc-fit-Galactic}
\end{figure*}

\begin{table}
  \centering
  \caption{Bounds of allowed values for parameters in model fits}
  \label{tab:parameter-ranges}
  \newlength\partabwidth
  \setlength\partabwidth{0.7\linewidth}
  \begin{tabular*}{\partabwidth}{@{\extracolsep{\fill}}l rr}
    \toprule
    Parameter & Lower & Upper\\
    \midrule
    \(\sigma^2\) & \(0.25\, \max [B]\)& \(2\, \max [B]\)\\
    \(r_0\) & \(0.1\, L\) & \(2\, L\)\\
    \(m\) & \(0.5\) & \(2.0\) \\
    \(s_0\) & \SI{0.1}{arcsec}& \SI{1.5}{arcsec}\\
    \(B\noise\) & \(0\) & \(3\, \min [B]\) \\
    \bottomrule
    \multicolumn{3}{@{}p{\partabwidth}@{}}{
    Note: \(\max[B]\) and \(\min[B]\) are over all bins in the observed structure function.
    }
  \end{tabular*}
\end{table}

@@

\input{SFresults}

@@

For the observational values (blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).

@@

The posterior distributions of model parameters
that are consistent with the observations for each region are estimated
using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
A uniform prior distribution is assumed between upper and lower bounds
for each parameter, as given in Table~\ref{tab:parameter-ranges}.
To help ensure convergence of the MCMC algorithm,
we used chain lengths that exceeded \num{50} times the
estimated autocorrelation length for each parameter,
which required \num{50000} to \num{150000} samples,
depending on the source.
Thin translucent lines in the figures show structure functions using the parameters of
a random selection of \num{100} posterior samples from the MCMC chain,
both for \(\tilde{B}(r)\) orange and \(B(r)\) (green).
This gives an estimate in the uncertainty about the best-fit model.
Credibility intervals for the parameters are estimated from percentiles
of the posterior distribution and are indicated in the figures by shaded gray boxes
around the best-fit parameter values
(heavy shading for 68\% interval; light shading for 95\% interval).
The 95\% credibility interval for each parameter and for each source
is also given in Table~\ref{tab:Res}.
Figure~\ref{fig:corner-example-Orion} gives an example for Orion of
the pairwise correlations in the posterior distributions of the model parameters,
plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
Corresponding plots for the remaining sources are given in Appendix~\ref{sec:addit-covar-corn}.

@@

@@

%structure functions plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. 
In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
The points left our correspond to the largest separations that are not consider in our model. 
In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B\noise\).
These values were obtained using the LM method.
For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.

For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the others. 
Instead, the discrete fiber positions are diversely located across the FOV.
This would affect the structure function since the values are not adjacent as the other observations.
This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.

%corner plots descriptions
Figures \ref{fig:corner-example-Orion} show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints
(further examples in Appendix~\ref{sec:addit-covar-corn}).
These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.

Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
The confidence intervals for these values are up to 2-sigma of the posteriors.
The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
The \(B\noise\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
The fourth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
The fifth column shows the correlation value \(r_0\) in parsecs.
The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
The sixth column indicates the size of each observational box in parsecs.
The index \(m\) is shown in the seventh column.
The range covered by the power-law index goes from 0.7 to 1.5.
The eighth column show the ratio \(L / r_0\)
The last column shows the FWHM seeing in arcsec.
%The interpretation of our results is developed in the next section.

@@

\section{\boldmath Notes on individual \hii{} regions}
\label{sec:notes-individual-hii}
For each region or pair of regions in our sample,
we give a more description of its physical properties
(supplementing section~\ref{sec:regions-milky-way})
together with additional details of the model fit to the structure function
(supplementing section~\ref{sec:results}).

@@

Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
Valid scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first three points of the structure function.
From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.

The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-Galactic}c.
This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}.

@@

The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first two points.
The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

@@

(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
For this region we merge the first two points of the structure function.
As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).

@@

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
In this case we merge the first five points of the structure function.
The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

@@

The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
In this case we merge the first three points of the structure function.
The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
For this region the first ten points lie below the true model.
At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

\subsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%Note to me: incomplete section. Find more regions info and finish asap.
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.

@@

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
All the structure function points lies below the true model.
The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.

@@

NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
For the northern cluster they find eight luminous stars and no evolved massive stars.
More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.

This suggest that two episodes of star formation, at least, have taken place in the GEHR.

@@

\begin{figure*}
  \centering
  \sfcfigggg{OrionS}{M8}{OrionLH}{CarC}
  \caption{
    Corner plots of covariances between
    fitted model parameters
    of \ha{} structure function
    for Galactic \hii{} regions.
  }
  \label{fig:corner-Galactic}
\end{figure*}

@@

>>>>

\begin{figure*}
  \centering
  \sffigggg{OrionS}{OrionLH}{M8}{CarC}
  \caption{
    Second-order structure functions
    for velocity centroid images
    of the \ha{} emission line
    from Galactic \hii{} regions.
    Blue symbols show the observed mean structure function
    in each radial bin.
  }
  \label{fig:strucfunc-fit-Galactic}
\end{figure*}

\begin{table}
  \centering
  \caption{Bounds of allowed values for parameters in model fits}
  \label{tab:parameter-ranges}
  \newlength\partabwidth
  \setlength\partabwidth{0.7\linewidth}
  \begin{tabular*}{\partabwidth}{@{\extracolsep{\fill}}l rr}
    \toprule
    Parameter & Lower & Upper\\
    \midrule
    \(\sigma^2\) & \(0.25\, \max [B]\)& \(2\, \max [B]\)\\
    \(r_0\) & \(0.01\, L\) & \(2\, L\)\\
    \(m\) & \(0.5\) & \(2.0\) \\
    \(s_0\) & \SI{0.1}{arcsec}& \SI{1.5}{arcsec}\\
    \(B\noise\) & \(0\) & \(3\, \min [B]\) \\
    \bottomrule
    \multicolumn{3}{@{}p{\partabwidth}@{}}{
    Note: \(\max[B]\) and \(\min[B]\) are over all bins in the observed structure function.
    }
  \end{tabular*}
\end{table}

@@

\input{table-results}

@@

For the observational values (blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
This \(L/2\) constrain is not used for the regions observed with MUSE.

@@

The posterior distributions of model parameters
that are consistent with the observations for each region are estimated
using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
A uniform prior distribution is assumed between upper and lower bounds
for each parameter, as given in Table~\ref{tab:parameter-ranges}.
To help ensure convergence of the MCMC algorithm,
we used chain lengths that exceeded \num{50} times the
estimated autocorrelation length for each parameter,
which required \num{50000} samples.
Thin translucent lines in the figures show structure functions using the parameters of
a random selection of \num{100} posterior samples from the MCMC chain,
both for \(\tilde{B}(r)\) orange and \(B(r)\) (green).
This gives an estimate in the uncertainty about the best-fit model.
Credibility intervals for the parameters are estimated from percentiles
of the posterior distribution and are indicated in the figures by shaded gray boxes
around the best-fit parameter values
(heavy shading for 68\% interval; light shading for 95\% interval).
The 95\% credibility interval for each parameter and for each source
is also given in Table~\ref{tab:Res}.
Figure~\ref{fig:corner-example-Orion} gives an example for Orion of
the pairwise correlations in the posterior distributions of the model parameters,
plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
Corresponding plots for the remaining sources and a table for the fitting parameters are given in Appendix~\ref{sec:addit-covar-corn}.

@@

Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
The derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
than the box size, which is the minimum value for this ratio of our sample. 
Hence we can confirm that the finite map has no effect in our results.
The derived seeing parameter \(s_0 = \SI{0.002}{pc}\), consistent with the Orion core fit, is more than \num{250} times smaller than \(r_0\).
This large ratio is because the separation of the pixels for the EON observations are at separations above the observational seeing, so these parameter has virtually no effect in our model for the EON case.
The previous statement can be confirmed with the Fig. \ref{fig:corner-Galactic}b which shows the corner plot for the EON.
The RMS seeing posterior is flat, meaning that the values in that range doesn't modify the fit.

This behavior is also seen in the Carina nebula and Lagoon nebula.
The observations for this regions are from the FLAMES multi-fiber instrument (section \ref{sec:flames-multi-fiber} ) in which the fibers separation  (see Figure \ref{fig:velocity-maps}) is above the observational seeing for the regions.

@@

%structure functions plots descriptions
%Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. 
%In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
%The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
%The points left our correspond to the largest separations that are not consider in our model. 
%In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
%The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
%The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.

%Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
%The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
%The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B\noise\).
%These values were obtained using the LM method.
%For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
%The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.

%For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
%We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the others. 
%Instead, the discrete fiber positions are diversely located across the FOV.
%This would affect the structure function since the values are not adjacent as the other observations.
%This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.

%corner plots descriptions
%Figures \ref{fig:corner-example-Orion} show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints
%(further examples in Appendix~\ref{sec:addit-covar-corn}).
%These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
%They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
%The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
%A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.

%Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
%The confidence intervals for these values are up to 2-sigma of the posteriors.
%The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
%The \(B\noise\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
%The fourth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
%The fifth column shows the correlation value \(r_0\) in parsecs.
%The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
%The sixth column indicates the size of each observational box in parsecs.
%The index \(m\) is shown in the seventh column.
%The range covered by the power-law index goes from 0.7 to 1.5.
%The eighth column show the ratio \(L / r_0\)
%The last column shows the FWHM seeing in arcsec.
%The interpretation of our results is developed in the next section.

@@

\section{\boldmath Notes on individual \hii{} regions}
\label{sec:notes-individual-hii}
For each region or pair of regions in our sample,
we give a more description of its physical properties
(supplementing section~\ref{sec:regions-milky-way})
together with additional details of the structure function
(supplementing section~\ref{sec:results}).

%the model fit to

@@

Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
In this case we merge the first three points of the structure function.
%From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
%The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.

@@

The Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
%There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first two points.
The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
%The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

@@

(The Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
%The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there are just a couple of points that lie below the true model, indicating that the majority of points isn't affected by the seeing.
For this region we merge the first two points of the structure function.
As the Lagoon nebula, Carina also shows a non-uniform behavior below the correlation length.
%The correlation length is \SI{0.56}{pc} pc at a \(\sigma^2\pos\) of \SI{18}{km^{2}.s^{-2}} and an index of \num{1.14}.
At larges scales the structure function of the Carina nebula follows a pattern that resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions shows a small amplitude periodic pattern around 2\(\sigma^2\pos\).

@@

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-MC}a.
In this case we merge the first five points of the structure function.
%The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one %point of the structure function is below this value.
%Until a separation of \SI{1.7}{pc} is reached, the structure function lies below the true model.
%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{297 \pm 9}{km^{2}.s^{-2}} and an index of \num{0.85}.
At large separations 30 Doradus structure function presents a behavior of tapered fluctuations. The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

@@

The Figure~\ref{fig:strucfunc-fit-MC}b shows the structure function of NGC 346.
%In this case we merge the first three points of the structure function.
%The seeing value is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}).
For this region the first ten points lie below the true model.
At separations above \SI{0.4}{pc} the observed structure functions is coincident with the true model. 
%The correlation length is \SI{2}{pc} at a \(\sigma^2\pos\) of \SI{35}{km^{2}.s^{-2}} and an index of \num{0.80}.
For scales above \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function shows a pattern of ascending values until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

\subsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.

@@

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}a we show the structure function of Hubble V.
For the observations coming from the TAURUS-II instrument there wasn't any merging of points at small scales.
%The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
%All the structure function points lies below the true model.
%The correlation length is \SI{3.5}{pc} at a \(\sigma^2\pos\) of  \SI{10}{km^{2}.s^{-2}} and an index of \num{0.75}.
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until it reaches \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}}.
Finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-ExtraGal}b.
%The seeing is \SI{0.6}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
%The correlation length is \SI{4}{pc} at a \(\sigma^2\pos\) of \SI{15}{km^{2}.s^{-2}} and an index of \num{0.93}.
A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}.

@@

NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
For the northern cluster they find eight luminous stars and no evolved massive stars.
More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
This suggest that two episodes of star formation, at least, have taken place in the GEHR.

@@

\begin{figure*}
  \centering
  \sfcfigggg{OrionS}{OrionLH}{M8}{CarC}
  \caption{
    Corner plots of covariances between
    fitted model parameters
    of \ha{} structure function
    for Galactic \hii{} regions.
  }
  \label{fig:corner-Galactic}
\end{figure*}

@@

\input{table-fit-parameters}
